\chapter{Conclusion}
The initial goal of this thesis was to find a simple way of estimating parameters of solar PV installations and this goal has been accomplished with moderate success. Some of the algorithms are thousands of lines of long, but the underlying mathematics was still kept simple. As a result, the code can be understood and modified by a wider audience. This is in particular contrast with AI and machine learning based approaches which often provide good results but which tend to be less insightful.

From the perspectives of mathematics and programming, model fitting problems are not particularly difficult. In this thesis, the challenges rose from optimization, understanding patterns in the data and discovering where the limits of the estimation algorithms come from. The insights gained while tackling these issues may be more valuable to other researchers than the final estimation algorithms. The most significant of which are the center angle error function, Fibonacci-lattice based angle space discretization and angle space resolution estimates. These were not mentioned in the cited literature and while the are most likely already used in other fields, they would most likely prove to be useful for similar studies conducted in the future.

While experimenting with the datasets, some interesting traits and phenomena were observed, some of which could warrant their own studies. For example, the figure \ref{10kkuopioplot} shows that the last hours of the specific day are noisy. This noise may play a significant role in the prediction erros and thus further studies in detection and classification of noise types in solar PV datsets would prove to be useful for all who perform analysis on solar PV installations. Perhaps the largest apparent obstacle in noise detection and classification studies is the temporal resolution as noise profiles of clouds, shadowing structures or temperature fluctuations may prove to be impossible to detect accurately at low temporal resolutions.

Lastly I would like to encourage other researchers to publish their research and code openly. During preminary research and literature reviews, the code examples or datasets which were used for research papers did not seem to be available. While research code may not be useful as is, 


 open research should be encouraged. During preminary research and literature reviews, there did not seem to be 

Lastly the state of open source research is somewhat concerning. Solar energy plays a significant role in green energy transition and 
